Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-09-09 writeup/conStruct.tex
G'c changes

\newpage
\section*{Introduction}
A fundamental quandary in the description of biological diversity is
the fact that diversity shows both discrete and continuous patterns. 
For example, reasonable people can disagree about whether two 
populations are separate species, because the 
process of speciation is usually gradual, and so there is no set point
in the continuous divergence of populations when they unambiguously become discrete species.
The issue of identifying meaningful biological subunits 
extends below the species level, as patterns of phenotypic
and genetic diversity within and among populations are shaped
by continuous migration and drift, as well as by more discrete events, 
such as geographic barriers, rapid expansions, bottlenecks, and rare
long distance migration.

@@

There have been many methods proposed to characterize population
genetic structure,
including generating population phylogenies \citep{CavalliSforza1975, treemix},
dimensionality-reduction approaches \citep{meirmans2009genodive}, 
such as principal components analysis 
\citep{menozzi1978synthetic,novembre_interpreting_2008, price2006eigenstrat},
and model-based clustering approaches 
\citep[e.g.][]{STRUCTURE, falush2003, hubisz2009,ADMIXTURE, 
FINESTRUCTURE, fastStructure, huelsenbeck2007inference, 
Corander2003,TESS,geneland}, among others.
Here, we will focus on model-based clustering, the most widely used class of approaches for population delineation.
Existing model-based clustering methods model each individual's genotypes 
as random draws from a set of underlying, unobserved population clusters, 
each with a characteristic set of allele frequencies, which are estimated. 
These underlying frequencies are identical 
for all individuals assigned to a cluster, 
\emph{regardless} of their spatial location. 
Spatial information has been incorporated into some of these methods, 
by, for example, placing spatial priors on cluster memberships \citep{geneland}, 
but this does not address the underlying issue that 
these methods assume that allele frequencies 
are constant in a cluster across the species' range.  
Like the method we present here, these are based on a statistical model,
but do not perform inference directly with a demographic model.
Each of these methods perform best in particular situations,
but all can give misleading results when applied to data that show a continuous pattern of isolation by distance 
\citep{Wright1943, novembre_interpreting_2008, Frantz2009}.

@@

\subsection*{Simulations}
We first test the method with scenarios generated using the coalescent simulator \texttt{ms} \citep{Hudson2002}.
To generate discrete population structure, we simulate $K$ distinct populations,
each of which split from a common ancestor $\tau_{\text{s}}$ units of coalescent time in the past,
without subsequent migration between them.
To generate continuous differentiation within each cluster,
at time $\tau_{\text{e}}$ in the past,
each of these discrete clusters instantaneously colonizes a lattice of demes,
for which we use a stepping stone model with symmetric migration 
to nearest neighbors (eight neighbors, including diagonals).
Finally, at time $\tau_{\text{a}}$ in the past 
we generate a single dataset 
by collapsing those $K$ discrete lattices into a single grid of demes that are admixed to various degrees from these different layers.
(see Fig \ref{sim_setup}).
We simulated datasets using $K=1$, 2, and 3 layers,
in each sampling 10,000 unlinked loci from each of 20 haploid individuals from every deme.

@@

A number of results are immediately clear from these tests with simulated data.
First, \texttt{conStruct} performs well on all simulated scenarios.
Across all values of K and for all simulations, 
the spatial model is correctly preferred over the nonspatial model (Fig \ref{sim_xvals})., 
and it infers the true admixture proportions with high accuracy, tight precision, and good coverage 
(Figs \ref{simK2_adprop_fit} and \ref{simK3_adprop_fit}).
Second, the predictive accuracy of the nonspatial model increases 
with the number of clusters in the model, 
as it describes continuous, spatial patterns of relatedness between demes within the same cluster 
using gradients of admixture across more and more discrete clusters.
This behavior of the nonspatial model is highlighted in 
the analyses of data simulated under $K=1$ (Fig \ref{simK1_pies} and \ref{simK1_nsp_pies}):
as $K$ in the model increases, 
the sampled area is increasingly divvied up between clusters 
with ``centers of mass" in the $K$ geographical extremes of the simulated space.
At $K=2$, the clusters are centered in opposite corners on the map; 
at $K=3$, in the lower two corners and the top half; 
at $K=4$, all four corners, and so on.
These results are qualitatively similar to those generated using fastSTRUCTURE \citep{fastStructure}, 
which also describes continuous differentiation using admixture between clusters
 (Fig \ref{fastStr_simK1}-\ref{fastStr_simK3}).
While it is true that each cluster is more similar within itself
than it is to other clusters,
we know that these boundaries are arbitrary,
since the data were simulated with no such boundaries.

In contrast, the predictive accuracy of the spatial \texttt{conStruct} model
either plateaus at or declines from the true value of $K$ used to simulate the data 
(Figs \ref{sim_xvals}, \ref{simK1_xval}, \ref{simK2_xval}, and \ref{simK3_xval}).
And, as $K$ in the spatial model increases, 
deme membership in layers beyond the number used to simulate the data does not appreciably increase 
(Fig \ref{simK1_sp_pies}, \ref{simK2_sp_pies}, \ref{simK3_sp_pies}).
That is, even when the spatial model is run with $K=7$, 
the inferred admixture proportions are nearly identical to 
those estimated under the true value of $K$ for each simulation.
These results are highlighted in the calculation of layer importance for 
analyses run in each simulation (Fig \ref{simK1_laycon}, \ref{simK2_laycon}, and \ref{simK3_laycon}).
In the spatial analyses run using the true value of $K$,
the importance of the $K$ layers remains constant even with additional layers;
in contrast, additional layers in the nonspatial analyses continue to be important for describing variation.

@@

Our data, originally published by \cite{geraldes_etal_2014}, 
consist of 434 individuals sampled from 35 drainages 
and genotyped at just over 33,000 loci (map of the sampling shown in Fig \ref{populus_map}).
The data were generated using RAD-seq, 
and showed a strong pattern of bias in allelic dropout 
(the majority of missing data were from drainages with only \textit{Populus balsamifera} individuals).
To ameliorate some of the problems that arise when there is a strong bias in which data are missing, 
we dropped loci for which any data were missing, 
resulting in just over 20,200 loci retained for analysis.  
We then analyzed these data, grouped by drainage, using both the spatial and nonspatial \texttt{conStruct} models, 
using $K = 1$ through 7,
and compared these models using cross-validation.
The results of these analyses are shown in 
Figs \ref{populus_pies} and \ref{populus_xvals}, 
as well as in Figs \ref{populus_sp_pies} - \ref{populus_laycon} in the Supplementary Materials.

@@

All models with $K>1$ assigned the majority of each species
to distinct layers, with some populations drawing ancestry from multiple layers.
This provides strong support for discrete population structure between the two species,
with some admixture,
rather than a single, continuous cline of ancestry.
At all values of $K>1$, discrete population structure was mostly partitioned along species lines; 
at values of $K$ above 2, further discrete substructure was inferred within the \textit{P. trichocarpa} samples, 
while \bals{} samples displayed no substructure up to $K=7$.
This lack of substructure within the sampled \bals{} populations is largely in agreement with results from 
\citet{keller_etal_2010}, who found that \bals{} in the region is characterized by relatively low diversity, 
and probably represents a recent, postglacial expansion.

A consistent split between layers within \tri{} fell along the ``no-cottonwood belt," 
a region along the central coast of British Columbia in which black cottonwood is absent. 
The no-cottonwood belt is hypothesized to divide the species' distribution 
into northern and southern groups, which, in a provenance test, 
were experimentally shown to display different phenotypes 
\citep[e.g., pathogen resistance,][]{xie2009,xie2012}.  
At higher values of $K$, drainages at the southern tip of \tri{} sampling 
begin to split out into their own layers.  
This may potentially be the result of introgression from southern \textit{Populus} species, 
such as \textit{P. angustifolia} or \textit{fremontii} \citep{Zhou2012,geraldes_etal_2014}

At all values of $K$, the spatial model was preferred over the nonspatial model (Fig \ref{populus_xvals}).
Most of this signal seems to derive from the \textit{P. trichocarpa} samples:
covariance within predominantly \tri{} layers decays more quickly with distance
than within the majority \bals{} layer, as seen in Fig \ref{populus_sp_clst_covs}.  
This indicates that, although isolation by distance is a feature of the dataset as a whole, 
its magnitude varies considerably across biological units - 
an aspect of the data \texttt{conStruct} is able capture well.

\subsubsection*{Black bears}
The American black bear, \textit{Ursus americanus}, is endemic to North America
and has a broad distribution across the continent.
During the last glacial maximum, 
black bears were confined to isolated glacial refugia, 
from which they subsequently expanded to occupy their current range
\citep{WoodingWard1997,Byun1997,Stone2000,Puckett2015}.
The retreat of the glaciers was relatively recent in units of 
black bear generation times \citep{Onorato2004}, 
so we might reasonably expect the divergence accrued between refugia 
to be reflected in discrete genetic structure between extant populations.
Black bears are strong dispersers \citep{Moore2014}, 
but they are distributed across most of the continent, 
so we may therefore expect them to experience distance-limited 
mating opportunities and exhibit a pattern of IBD.
As with the poplars described above, 
this system is likely to present patterns of genetic structure 
that are both continuous and discrete, 
making it well-suited as a test for our method.
We organize the results of our analyses of 
the complicated landscape of genetic structure in black bears 
around the following questions:
\begin{enumerate}
\item How many historical clusters are reflected in modern patterns of genetic variation?
\item Do we see support for a pattern of isolation by distance within each of the inferred discrete groups?
\end{enumerate}

@@

Bears in the sample are partitioned into two main groups:
one to the east of the Rocky Mountains, 
which also occurs in Alaska, and, presumably, 
in the intervening (unsampled) northern Great Plains and Canadian Shield;
the other primarily west of the Rockies, 
but presumably stretching up into British Columbia.
Additional layers in the spatial model have strong statistical support 
up until around $K=5$ or 6 (Fig \ref{bear_xvals}).
However, upon examining layer importance (Fig \ref{bear_laycon}),
it is clear that the additional layers beyond $K=2$ are contributing only a very small amount toward 
total covariance between individuals.
The locations of the individuals inferred to be admixed between the two layers 
provide information about a possible zone of contact and migration between these groups 
along the northwestern coast of North America and near the Cascade Range in the northern U.S.
These findings are consistent with a scenario of postglacial expansion from two refugia, 
one in the American Southwest and one in the American Southeast, 
but lack of any samples from Canada and Mexico, 
and lack of denser sampling across northern North America, 
make more detailed interpretations untrustworthy.
In addition, our model is not an explicit test of any demographic scenario, 
and also uses a dataset that consists solely of nuclear (rather than mitochondrial) DNA.

@@

The pattern of isolation by distance is ubiquitous in nature;
this is unsurprising, as mating opportunities are distance-limited in most species.
This common pattern can flummox commonly used clustering methods, 
which must use a possibly large number of discrete clusters
to describe such continuous population differentiation.
Inference of these spurious clusters can have implications for 
downstream analysis and interpretation of genetic data, 
including conservation management decisions and 
identification of the genetic basis of adaptation or disease traits.

In this paper, we have presented a statistical framework, \texttt{conStruct}, for simultaneously 
modeling continuous and discrete patterns of population structure.
By employing the sensible default assumption
that relatedness ought to decay with distance, even within a population, 
we avoid erroneously ascribing population differentiation to discrete population clusters.
We also present a cross-validation approach for comparing between models, 
although we stress the limits of this or any model selection procedure for genetic clustering.

The method performs well on simulated data:
we accurately infer the admixture proportions used to simulate the data 
and accurately pick the simulating model as the best model using our cross-validation procedure.
Empirical applications of \texttt{conStruct} to a sample of North American poplars 
and a sample of North American black bears yield reasonable results.

@@

\paragraph{Comparison to nonspatial model-based clustering}
Above, we showed that 
(a) the nonspatial \texttt{conStruct} model recapitulates results of 
other, commonly-used nonspatial clustering methods,
and 
(b) \texttt{conStruct} can concisely capture spatial structure, which is nearly always expected within clusters.
Given this, when should methods without spatial capability be used?
One advantage these have over \texttt{conStruct} is speed.
Although \texttt{conStruct}'s computation time is invariant 
with the number of loci included in the dataset 
(after the initial calculation of the allelic covariance), 
it scales poorly with number of samples.
The computationally limiting step is the inversion of the parametric covariance, 
which is an operation of order $O(n^3)$, 
whereas computation time for, e.g., STRUCTURE, 
scales linearly with number of samples. \gb{is this true?}
The other main difference is the model of noise,
but it is unclear what effects this may have,
or indeed, which is closer to the truth.

>>>>

\newpage
\section*{Introduction}
A fundamental quandary in the description of biological diversity is
the fact that diversity shows both discrete and continuous patterns. 
For example, reasonable people can disagree about whether two 
populations are separate species, because the 
process of speciation is usually gradual, and so there is no set point
in the continuous divergence of populations when they unambiguously become discrete species.
The issue of identifying meaningful biological subunits 
extends below the species level, as patterns of phenotypic
and genetic diversity within and among populations are shaped
by continuous migration and drift, as well as by more discrete events, 
such as geographic barriers, rapid expansions, bottlenecks, and rare
long-distance migration.

@@

There have been many methods proposed to characterize population
genetic structure,
including generating population phylogenies \citep{CavalliSforza1975, treemix},
dimensionality-reduction approaches \citep{meirmans2009genodive}, 
such as principal components analysis 
\citep{menozzi1978synthetic,novembre_interpreting_2008, price2006eigenstrat},
and model-based clustering approaches 
\citep[e.g.][]{STRUCTURE, falush2003, hubisz2009,ADMIXTURE, 
FINESTRUCTURE, fastStructure, huelsenbeck2007inference, 
Corander2003,TESS,geneland}, among others.
\gc{Each of these methods perform best in particular situations,
but many can give misleading results when applied to data that show a continuous pattern of isolation by distance 
\citep{Wright1943, novembre_interpreting_2008, Frantz2009}.}
Here, we will focus on model-based clustering, the most widely used class of approaches for population delineation.
Existing model-based clustering methods model each individual's genotypes 
as random draws from a set of underlying, unobserved population clusters, 
each with a characteristic set of allele frequencies, which are estimated. 
These underlying frequencies are identical 
for all individuals assigned to a cluster, 
\emph{regardless} of their spatial location. 
Spatial information has been incorporated into some of these methods, 
by, for example, placing spatial priors on cluster memberships \citep{geneland,TESS}, 
but this does not address the underlying issue that 
these methods assume that allele frequencies 
are constant in a cluster across the species' range.  
%Like the method we present here, these are based on a statistical model,
%but do not perform inference directly with a demographic model.

@@

\subsection*{Simulations}
We first test the method with scenarios generated using the coalescent simulator \texttt{ms} \citep{Hudson2002}.
To generate discrete population structure, we simulate $K$ distinct populations,
each of which split from a common ancestor $\tau_{\text{s}}$ units of coalescent time in the past,
without subsequent migration between them.
To generate continuous differentiation within each cluster,
at time $\tau_{\text{e}}$ in the past,
each of these discrete clusters instantaneously colonizes an
\gc{independent} lattice of demes,
for which we use a stepping stone model with symmetric migration 
to nearest neighbors (eight neighbors, including diagonals).
Finally, at time $\tau_{\text{a}}$ in the past 
we generate a single dataset 
by collapsing those $K$ discrete lattices into a single grid of demes that are admixed to various degrees from these different layers.
(see Fig \ref{sim_setup}). \gc{We collapse the layers together using
random admixture proportions that are spatially autocorrelated  (see
{\bf XXXX} for details), so
that both the frequencies in clusters and the cluster memberships are
spatially autocorrelated.} We simulated datasets using $K=1$, 2, and 3 layers,
in each sampling 10,000 unlinked loci from each of 20 haploid individuals from every deme.

@@

A number of results are immediately clear from these tests with simulated data.
First, \texttt{conStruct} performs well on all simulated scenarios.
Across all values of K and for all simulations, 
the spatial model is correctly preferred over the nonspatial model
(Fig \ref{sim_xvals}). Second, the predictive accuracy of the nonspatial model increases 
with the number of clusters in the model, 
as it describes continuous, spatial patterns of relatedness between demes within the same cluster 
using gradients of admixture across more and more discrete clusters.
This behavior of the nonspatial model is highlighted in 
the analyses of data simulated under $K=1$ (Fig \ref{simK1_pies} and \ref{simK1_nsp_pies}):
as $K$ in the model increases, 
the sampled area is increasingly divvied up between clusters 
with ``centers of mass" in the $K$ geographical extremes of the simulated space.
At $K=2$, the clusters are centered in opposite corners on the map; 
at $K=3$, in the lower two corners and the top half; 
at $K=4$, all four corners, and so on.
These results are qualitatively similar to those generated using fastSTRUCTURE \citep{fastStructure}, 
which also describes continuous differentiation using admixture between clusters
 (Fig \ref{fastStr_simK1}-\ref{fastStr_simK3}).
While it is true that each non-spatial cluster is \gc{genetically} more similar within itself
than it is to other clusters,
we know that these boundaries are arbitrary,
since the data were simulated with no such boundaries.

In contrast, the predictive accuracy of the spatial \texttt{conStruct} model
either plateaus at or declines from the true value of $K$ used to simulate the data 
(Figs \ref{sim_xvals}, \ref{simK1_xval}, \ref{simK2_xval}, and \ref{simK3_xval}).
And, as $K$ in the spatial model increases, 
deme membership in layers beyond the number used to simulate the data does not appreciably increase 
(Fig \ref{simK1_sp_pies}, \ref{simK2_sp_pies}, \ref{simK3_sp_pies}).
\gc{Even} when the spatial model is run with $K=7$, 
the inferred admixture proportions are nearly identical to 
those estimated under the true value of $K$ for each simulation.
\gc{Moreover, the method infers the true admixture proportions with high accuracy, tight precision, and good coverage 
(Figs \ref{simK2_adprop_fit} and \ref{simK3_adprop_fit}).}

\gc{Finally, we calculated} of layer importance for 
analyses run in each simulation (Fig \ref{simK1_laycon}, \ref{simK2_laycon}, and \ref{simK3_laycon}).
In the spatial analyses, \gc{once we pass the true $K$, subsequent
layers add little in terms of (co)variance explained}  %$K$ layers remains constant even with additional layers;
in contrast, additional layers in the nonspatial analyses continue to
be important for describing variation, \gc{as they are forced to partition
up the spatial patterns within clusters}.

@@

Our data, \gc{from} \cite{geraldes_etal_2014}, 
consist of 434 individuals sampled from 35 drainages 
and genotyped at just over 33,000 loci (map of the sampling shown in Fig \ref{populus_map}).
The data were generated using RAD-seq, 
and showed a strong pattern of bias in allelic dropout 
(the majority of missing data were from drainages with only \textit{Populus balsamifera} individuals).
To ameliorate some of the problems that arise when there is a strong bias in which data are missing, 
we dropped loci for which any data were missing, 
resulting in just over 20,200 loci retained for analysis.  
We then analyzed these data, grouped by drainage, using both the spatial and nonspatial \texttt{conStruct} models, 
using $K = 1$ through 7,
and compared these models using cross-validation.
The results of these analyses are shown in 
Figs \ref{populus_pies} and \ref{populus_xvals}, 
as well as in Figs \ref{populus_sp_pies} - \ref{populus_laycon} in the Supplementary Materials.

@@

All models with $K>1$ assigned the majority of each \gc{of the two} species
to distinct layers, with some populations drawing ancestry from multiple layers.
This provides strong support for discrete population structure between the two species,
with some admixture,
rather than a single, continuous cline of ancestry.
At all values of $K>1$, discrete population structure was mostly partitioned along species lines; 
at values of $K$ above 2, further discrete substructure was inferred within the \textit{P. trichocarpa} samples, 
while \bals{} samples displayed no substructure up to $K=7$.
This lack of substructure within the sampled \bals{} populations is largely in agreement with results from 
\citet{keller_etal_2010}, who found that \bals{} in the region is characterized by relatively low diversity, 
and probably represents a recent, postglacial expansion.

\gc{For values of $K<4$,} the spatial model was strongly preferred over the nonspatial model (Fig \ref{populus_xvals}).
Most of this signal seems to derive from the \textit{P. trichocarpa} samples:
covariance within predominantly \tri{} layers decays more quickly with distance
than within the majority \bals{} layer, as seen in Fig \ref{populus_sp_clst_covs}.  
This indicates that, although isolation by distance is a feature of the dataset as a whole, 
its magnitude varies considerably across biological units - 
an aspect of the data \texttt{conStruct} is able capture well.
\gc{Based on our cross-validation results we view $K=3$ spatial-model
  as sufficient description of the data.}

A consistent split between layers within \tri{} fell along the ``no-cottonwood belt," 
a region along the central coast of British Columbia in which black
cottonwood is absent \gc{(the break between yellow and red, for $K \geq 3$)} . 
The no-cottonwood belt is hypothesized to divide the species' distribution 
into northern and southern groups, which, in a provenance test, 
were experimentally shown to display \gc{differences in ecologically relevant} phenotypes 
\citep[e.g., pathogen resistance,][]{xie2009,xie2012}.  
At higher values of $K$, drainages at the southern tip of \tri{} sampling 
begin to split out into their own layers.  
This may potentially be the result of introgression from southern \textit{Populus} species, 
such as \textit{P. angustifolia} or \textit{fremontii} \citep{Zhou2012,geraldes_etal_2014}

\subsubsection*{Black bears}
The American black bear, \textit{Ursus americanus}, is endemic to North America
and has a broad distribution across the continent.
During the last glacial maximum, 
black bears were confined to isolated glacial refugia, 
from which they subsequently expanded to occupy their current \gc{range
\citep{WoodingWard1997,Byun1997,Stone2000,Puckett2015}.
%The retreat of the glaciers was relatively recent in units of 
%black bear generation times \citep{Onorato2004}, 
%so we might reasonably expect the divergence accrued between refugia 
%to be reflected in discrete genetic structure between extant populations.
%Black bears are strong dispersers \citep{Moore2014}, 
%but they are distributed across most of the continent, 
%so we may therefore expect them to experience distance-limited 
%mating opportunities and exhibit a pattern of IBD.
As} with the poplars described above, 
this system is likely to present patterns of genetic structure 
that are both continuous and discrete, 
making it well-suited as a test for our method.
We organize the results of our analyses of 
the complicated landscape of genetic structure in black bears 
around the following questions:
\begin{enumerate}
\item How many historical clusters are reflected in modern patterns of genetic variation?
\item Do we see support for a pattern of isolation by distance within each of the inferred discrete groups?
\end{enumerate}

@@

Bears in the sample are partitioned into two main groups \gc{($K \geq 2$)}:
one \gc{(red)} to the east of the Rocky Mountains, 
which also occurs in Alaska,
the other primarily west of the Rockies \gc{(blue)}.
\gc{The disjointed range of the blue layer, likely reflects the fact
that Canada was not sampled, and so the blue layer may extend
through the intervening (unsampled) northern Great Plains and Canadian
Shield, with the red layer presumably then stretching up into British Columbia.}

Additional layers in the spatial model have strong statistical support 
up until around $K=5$ or 6 (Fig \ref{bear_xvals}).
However, upon examining layer importance (Fig \ref{bear_laycon}),
it is clear that the additional \gc{spatial} layers beyond $K=2$ are contributing only a very small amount toward 
total covariance between individuals.
The locations of the individuals inferred to be admixed between the two layers 
provide information about a possible zone of contact and migration between these groups 
along the northwestern coast of North America and near the Cascade Range in the northern U.S.
These findings are consistent with a scenario of postglacial expansion from two refugia, 
one in the American Southwest and one in the American Southeast, 
but lack of any samples from Canada and Mexico, 
and lack of denser sampling across northern North America, 
\gc{make more detailed interpretations untrustworthy.}
%In addition, our model is not an explicit test of any demographic scenario, 
%and also uses a dataset that consists solely of nuclear (rather than
%mitochondrial) DNA. WHY DO WE CARE about BEAR MTDNS

@@

The pattern of isolation by distance is ubiquitous in nature;
this is unsurprising, as mating opportunities are distance-limited in most species.
This common pattern can flummox commonly used clustering methods, 
which must use a possibly large number of discrete clusters
to describe such continuous population differentiation.
Inference of these spurious clusters can have implications for 
downstream analysis and interpretation of genetic data, 
including conservation management decisions.

%and 
%identification of the genetic basis of adaptation or disease traits.

In this paper, we have presented a statistical framework, \texttt{conStruct}, for simultaneously 
modeling continuous and discrete patterns of population structure.
By employing the sensible default assumption
that relatedness ought to decay with \gc{geographic} distance, even within a population, 
we avoid erroneously ascribing population differentiation to discrete population clusters.
We also present a cross-validation approach for comparing between models, 
although we stress the limits of this or any model selection procedure for genetic clustering.

The method performs well on simulated data:
we accurately infer the admixture proportions used to simulate the data 
and accurately pick the simulating model as the best model using our cross-validation procedure.
Empirical applications of \texttt{conStruct} to a sample of North American poplars 
and a sample of North American black bears yield reasonable results,
\gc{and demonstrate that real datasets can better described using fewer
  layers, by acknowledging isolation by distance. }

@@

\paragraph{Comparison to nonspatial model-based clustering}
Above, we showed that 
(a) the nonspatial \texttt{conStruct} model recapitulates results of 
other, commonly-used nonspatial clustering methods,
and 
(b) \texttt{conStruct} can concisely capture spatial structure, which
\gc{will be common within} clusters.
Given this, when should methods without spatial capability be used?
One advantage these have over \texttt{conStruct} is speed.
Although \texttt{conStruct}'s computation time is invariant 
with the number of loci included in the dataset 
(after the initial calculation of the allelic covariance), 
it scales poorly with number of samples.
The computationally limiting step is the inversion of the parametric covariance, 
which is an operation of order $O(n^3)$, 
whereas computation time for, e.g., STRUCTURE, 
scales linearly with number of samples. \gb{is this true?}
The other main difference is the model of noise,
but it is unclear what effects this may have,
or indeed, which is closer to the truth.
